\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/discussion.tex
minor changes

\paragraph{Indirect Branch Predictor Barrier} - IBPB is used when transitioning to a new
address space, allowing a
program to ensure that earlier code's behavior does not effect its branch prediction.
IBPB requires CPU and operating system support. However, we observe on Linux that
processes running under the same user group do not receive IBPB protection,
enabling \speculake when the trigger and payload run under the same group.
Furthermore, IBPB does not prevent the speculative buffer overflow variant of
\speculake described in Section~\ref{subsec:spec-buffer-overflow}.

@@

\paragraph{Single Thread Indirect Branch Predictors} - STIBP prevents sibling
hyperthreads from interacting via the indirect branch predictor. However, this
does not prevent co-resident processes from cooperating when they run on the same
logical core.

\paragraph{Indirect Branch Restricted Speculation} - IBRS prevents code in less
privileged prediction modes from influencing indirect branch prediction in
higher privileges (e.g. the kernel). This does not
prevent speculative execution in a willing payload program in a less privileged
speculation mode.

\paragraph{Retpoline} is a software mitigation that replaces indirect jumps with
a special call/overflow/return sequence, controlling where the CPU will
speculate the indirect branch to a contained (and benign)
section~\cite{retpoline}. However, this defense is opt-in which \speculake
binaries could simply choose to not use, or alternatively use the unaffected
speculative buffer overflow variant.

@@

\subsubsection{Multiple Triggers}
To create further difficulties for an analyst, or to further target the
execution environment, it is possible to have the payload program to combine
multiple triggers. Instead of requiring only a single trigger program,
the payload could require multiple trigger programs to be running
simultaneously, or in a particular order. Alternatively, the payload could combine
trigger programs with input triggers, forcing an analyst to understand multiple
variants simulatenously.

>>>>

\paragraph{Indirect Branch Predictor Barrier}IBPB is used when transitioning to
a new address space, allowing a program to ensure that earlier code's behavior
does not effect its branch prediction. IBPB requires CPU and operating system
support. However, we observe on Linux that processes running under the same user
group do not receive IBPB protection, enabling \speculake when the trigger and
payload run under the same group. Furthermore, IBPB does not prevent the
speculative buffer overflow variant of \speculake described in
Section~\ref{subsec:spec-buffer-overflow}.

@@

\paragraph{Single Thread Indirect Branch Predictors}STIBP prevents sibling
hyperthreads from interacting via the indirect branch predictor. However, this
does not prevent co-resident processes from cooperating when they run on the
same logical core.

\paragraph{Indirect Branch Restricted Speculation}IBRS prevents code in less
privileged prediction modes from influencing indirect branch prediction in
higher privileges (e.g. the kernel). This does not
prevent speculative execution in a willing payload program in a less privileged
speculation mode.

\paragraph{Retpoline}is a software mitigation that replaces indirect jumps with
a special call/overflow/return sequence, controlling where the CPU will
speculate the indirect branch to a contained (and benign)
section~\cite{retpoline}. However, this defense is opt-in which \speculake
binaries could simply choose to not use, or alternatively use the unaffected
speculative buffer overflow variant.

@@

\subsubsection{Multiple Triggers}
To create further difficulties for an analyst, or to further target the
execution environment, it is possible to have the payload program to combine
multiple triggers. Instead of requiring only a single trigger program, the
payload could require multiple trigger programs to be running simultaneously, or
in a particular order. Alternatively, the payload could combine trigger programs
with input triggers, forcing an analyst to understand multiple variants
simultaneously.
